supplmental

### 2019-12-31 paper_stats.Rmd
change tables

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(pander)

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>% 
  pander()

@@

  pander(table_df)

@@

  pander(vrs_df)

>>>>

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(knitr)

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>% 
  kable()

@@

  kable(table_df)

@@

  kable(vrs_df)
